Proposed Solution

### 2017-01-25 CAV17/secs/abs.tex
stuff

System failures resulting from configuration errors 
are major reasons for compromised reliability of today's software
systems. Although a lot of program verification techniques 
have been proposed, verifying configuration files is still 
an open problem,
because 1) software configurations are typically written in
poorly structured and untyped ``languages'', and 
2) specifying rules for configuration 
verification is challenging in practice.

This paper presents \app, the first automatic verification framework for
general software configurations.
\app verifies a target configuration file $F$ through three steps.
First, \app parses a training set of configuration 
files (not necessarily correct) belonging to the same system as $F$,
translating these files to a
well-structured and probabilistically-typed 
intermediate representation.
Second, \app derives configuration rules by learning
these intermediate representations.
Finally, \app employs rule graph analysis to refine the 
resulting rules, and uses the refined rules to verify $F$.

\app is capable of detecting various configuration errors,
including ordering errors, integer correlation errors, type errors,
and missing entry errors. We evaluated \app by verifying 
public configuration files on github, and detected the above 
configuration errors in these widely-deployed files.

>>>>

System failures resulting from configuration errors 
are one of the major reasons for compromised reliability of today's software
systems. Although many techniques have been proposed for a 
configuration error
detection, these approaches mainly can be applied after an error has occurred. Verifying configuration files is, nevertheless, 
a challenging problem,
because 1) software configurations are typically written in
poorly structured and untyped ``languages'', and 
2) specifying rules for configuration 
verification is challenging in practice.
This paper presents \app, the first automatic verification framework for
general software configurations.
Our framework works as follows: in the pre-processing stage, we first automatically derive a specification.
Once we have a specification, we check if a given configuration file adheres to that specification.
The process of learning specification works through three steps.
First, \app parses a training set of configuration 
files (not necessarily all correct) into a
well-structured and probabilistically-typed 
intermediate representation.
Second, based on the association rule
learning algorithm \app learns rules from 
these intermediate representations. These rules are 
establishing relationships between the keywords appearing in the files. 
Finally, \app employs rule graph analysis to refine the 
resulting rules. \app is capable of detecting various configuration errors,
including ordering errors, integer correlation errors, type errors,
and missing entry errors. We evaluated \app by verifying 
public configuration files on Github, and we show that \app can 
detect known configuration errors in these files.
